---
title: "Adam C. Garber"
description: |
  A personal website by a teacher at Santa Barbara City College.!
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```

## Welcome 

Hi! My name is Adam Garber. I am a teacher at Santa Barbara City College.
I am interested in data science... [ADD Bio paragraph here]

## A question I care about

Write two or three sentences about a question, issue, or topic that matters
to you. Explain why it is interesting or important.

## Something I have learned with data

Write two or three sentences about one idea or skill from PSY 150 that you
could explain to someone outside this class.

[See my work on GitHub](https://adam-garber.github.io/)

```{r, echo=FALSE}

hist(
  mtcars$mpg,
  main = "Miles per gallon in the mtcars data",
  xlab = "Miles per gallon",
  col = "#7FC8C2",
  border = "white"
)
```